Visualization

### 2023-01-19 Code/NewPlots.Rmd
Data Update

graph_bts(cov, theta, target, width = 50)
ggsave('../Manuscript/plot_.1.pdf')
```
```{r}
theta <- 0.3
target <- c(0, 1, theta)
cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))

graph_bts(cov, theta, target, width = 25)
ggsave('../Manuscript/plot_.3.pdf')
```
```{r}
theta <- 0.5
target <- c(0, 1, theta)
cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))

graph_bts(cov, theta, target, width = 10)
ggsave('../Manuscript/plot_.5.pdf')
```

>>>>

graph_bts(cov, theta, target, width = 50)
ggsave('../Manuscript/figures/plot_.1.pdf')
```
```{r}
theta <- 0.3
target <- c(0, 1, theta)
cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))

graph_bts(cov, theta, target, width = 25)
ggsave('../Manuscript/figures/plot_.3.pdf')
```
```{r}
theta <- 0.5
target <- c(0, 1, theta)
cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))

graph_bts(cov, theta, target, width = 10)
ggsave('../Manuscript/figures/plot_.5.pdf')
```
